A systematic search for transiting planets using \KT

### 2015-02-05 ms.tex
Hand vetting notes

>>>>

There are many instrumental or astrophysical effects that can mimic a transit
signal in time series photometry.
For the primary \kepler\ mission, the noise induced by instrumental artifacts
on transit timescales was significantly smaller than transit depths for 
all but the smallest planets.
With \KT\ this is no longer the case.
The motion of the instrument causes a drift in the pointing of approximately
$1''$ per hour, causing variations in the flat field to dominate the 
photometric signal.

As a result, artifacts in the data induced by pointing jitter can ...

If the properties of the noise in the data can be fully understood and 
modeled, such artifacts can be separated from true astrophysical events.
Our model, however, makes no assumptions about the properties of the noise
other than that it is correlated across many stars on the detector.
Therefore, our model can occassionally be fooled by instrumental artifacts
that a more sophisticated method, or the human eye, can easily separate 
from true astrophysical signals.

To this end, we (euphamism for look at by eye) each system to identify the
most promising candidates.

\paragraph{False positives}
